---
title: "report-cursor-locationg"
output: 
  html_document:
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(ez)
library(apa)
library(base)
library(ggplot2)
library(dplyr)
library(reshape)
```
# Compare completion time among three settings
In this section, we test whether two visual enhancement techniques have significant impact to the completion time.
## Loading data
Variable "start" represents starting position of mouse pointer. 
```{r}
dataTime = read.csv(file = 'time.csv',  header = FALSE)
names(dataTime) = c('participant', 'start', 'target', 'tech', 'time')
```

## Evaluation
Through a quick scan of the raw data, we find some outliers. May be some participants failed to find the target during tasks or they are distracted. Before evaluating the data, we exclude outliers and plot the raw data from 12 participants.
```{r}
dataTimeFilt = dataTime %>%
  group_by(tech) %>%
  filter(!abs(time - mean(time)) > 3 * sd(time))

ggplot() + 
  geom_jitter(aes(interaction(tech), time), data = dataTimeFilt, colour = I("red"), position = position_jitter(width = 0.05)) + 
  scale_y_continuous(limits = c(1000, 6000)) + 
  theme(panel.background = element_blank(),
        panel.grid.major.y = element_line(size = .1, color = 'grey'))
```

## Run ANOVA on movement time
All trials are successfully recorded so there is no need for fitering. Since measuring performance in different background images and starting positions is not the concern of this poject, we aggregate the data by participant and tech.
```{r}
dataTimeAggr = dataTimeFilt %>%
  group_by(participant, tech) %>%
  summarise(time = mean(time))

# Convert the data using long format
dataTimeLong = melt(dataTimeAggr, id = c("participant", "tech", "time"))
```

Indicate the independent variables (visual enhancement techniques)
```{r}
dataTimeLong$tech = factor(dataTimeLong$tech)
```

Each participant uses all three techniques, we use repeated-measures ANOVA
```{r}
resultsTime = ezANOVA(dataTimeLong, dv=.(time), wid=.(participant), within=.(tech), detailed=TRUE)
kable(resultsTime$ANOVA)
```
More results from ANOVA
```{r}
kable(resultsTime$`Mauchly's Test for Sphericity`)
kable(resultsTime$`Sphericity Corrections`)
kable(anova_apa(resultsTime, sph_corr ="gg", print=FALSE))
```
Present some stats of the data
```{r}
kable(ezStats(dataTimeLong, dv=.(time), wid=.(participant), within=.(tech)))
```
## Interpretation of ANOVA
ANOVA shows there is no significant effect of visual enhancement techniques ($F_{2, 22}=2.4908, p = 0.1059, > 0.05, \eta_{p}^2=0.18$) on completion time. The average completion time is 2183ms for Ctrl-and-resizing, 2234ms for shaking-and-resizing and 2011ms for no visual enhancement. Mauchly’s Test for Sphericity is not statistically significant ($p = 0.7641$), we can't reject the null hypothesis that variance of the differences are equal.

## Some other analysis



# Analyze whether visual enhancement has significant impact to distance ratio
The section we analyze the influnce of two techniques on $\tau$, which is  the ratio between distance and displacement.
## Load data
```{r}
dataDist = read.csv('distance.csv', header=FALSE)
names = names(dataDist) = c('participant', 'start', 'target', 'tech', 'distanceRatio')
```

Similar to the previous analysis, we exclude outliers and plot raw data
```{r}
dataDistFilt = dataDist %>%
  group_by(tech) %>%
  filter(!abs(distanceRatio - mean(distanceRatio)) > 3 * sd(distanceRatio))

ggplot() + 
  geom_jitter(aes(interaction(tech), distanceRatio), data = dataDistFilt, colour = I("red"), position = position_jitter(width = 0.05)) + 
  scale_y_continuous(limits = c(0,7.5)) + 
  theme(panel.background = element_blank(),
        panel.grid.major.y = element_line(size = .1, color = 'grey'))
```

Then we aggregate the data and run ANOVA on distance ratio $\tau$
```{r}
dataDistAggr = dataDistFilt %>%
  group_by(participant, tech) %>%
  summarise(distanceRatio = mean(distanceRatio))

dataDistLong = melt(dataDistAggr, id = c("participant", "tech", "distanceRatio"))
dataDistLong$tech = factor(dataDistLong$tech)
resultsDist = ezANOVA(dataDistLong, dv=.(distanceRatio), wid=.(participant), within=.(tech), detailed=TRUE)
kable(resultsDist$ANOVA)
```
More results from ANOVA
```{r}
kable(resultsDist$`Mauchly's Test for Sphericity`)
kable(resultsDist$`Sphericity Corrections`)
kable(anova_apa(resultsDist, sph_corr ="gg", print=FALSE))
```
Some stats of the data
```{r}
kable(ezStats(dataDistLong, dv=.(distanceRatio), wid=.(participant), within=.(tech)))
```
## Interpretation of ANOVA
According to the results of ANOVA, techniques have significant impact to the distance ratio $\tau$ ($F_{2, 22}=16.7668, p < 0.05, \eta_{p}^2=0.6$). The result of auchly’s Test for Sphericity indicates that we can reject the null hypothesis and accept the alternative hypothesis: the variances of differences are not equal. Since we have three settings (Shaking, Ctrl, None), pairwise analysis is needed.

## Pairwise comparisons
```{r}
attach(dataDistLong)
pw <- pairwise.t.test(distanceRatio, tech, p.adj = "bonferroni")
detach(dataDistLong)
kable(pw$p.value)
```

# Plots presented in the report

This section shows figures in the report and our presentation
```{r}
library(Rmisc)
dataTimeSummary = summarySE(dataTimeFilt, measurevar = 'time', groupvars = 'tech')

p = ggplot(dataTimeSummary, aes(x = tech, y = time, fill=tech)) + 
  geom_bar(stat='identity', width=0.5, color="black", position=position_dodge()) + 
  geom_errorbar(aes(ymin=time-ci, ymax=time+ci), width=.2, position=position_dodge()) + 
  labs(title="Time(ms) for Move", x = "Techniques", y = "Time(ms)")
print(p)
```

```{r}
# Don't run this before analysis is done, it will mask other function
library(Rmisc)
dataDistSummary = summarySE(dataDistFilt, measurevar = 'distanceRatio', groupvars = 'tech')
p = ggplot(dataDistSummary, aes(x = tech, y = distanceRatio, fill=tech)) + 
  geom_bar(stat='identity', width=0.5, color="black", position=position_dodge()) + 
  geom_errorbar(aes(ymin=distanceRatio-ci, ymax=distanceRatio+ci), width=.2, position=position_dodge()) + 
  labs(title="Distance Ratio", x = "Techniques", y = "Distance Ratio")
print(p)
```

